---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# SpatioTemporal.cluster

<!-- badges: start -->
[![AppVeyor build status](https://ci.appveyor.com/api/projects/status/github/kongdd/heatwave?branch=master&svg=true)](https://ci.appveyor.com/project/kongdd/heatwave)
[![Travis build status](https://travis-ci.org/kongdd/heatwave.svg?branch=master)](https://travis-ci.org/kongdd/heatwave)
[![Codecov test coverage](https://codecov.io/gh/kongdd/heatwave/branch/master/graph/badge.svg)](https://codecov.io/gh/kongdd/heatwave?branch=master)
<!-- badges: end -->

The goal of SMI is to ...

## Installation

You can install the released version of SMI from [CRAN](https://CRAN.R-project.org) with:

``` r
devtools::install_github("kongdd/SpatioTemporal.cluster")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(SpatioTemporal.cluster)
## basic example code
```

## References

- Samaniego et al. (2013), "Implications of Parameter Uncertainty on Soil Moisture Drought Analysis in Germany", J Hydrometeor, 2013 vol. 14 (1) pp. 47-68. http://journals.ametsoc.org/doi/abs/10.1175/JHM-D-12-075.1

- Samaniego et al. (2018), "Anthropogenic warming exacerbates European soil moisture droughts", Nature Climate change, 2018 pp. 1-9. http://dx.doi.org/10.1038/s41558-018-0138-5
